---
title: "homework9"
author: "Nathan Frank and Yen Wang"
date: "3/30/2022"
output: html_document
---

Team members: Nathan Frank and Yen Wang
Link to repo: https://github.com/natefrank48/homework9 



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

Data Tidying

```{r}
av <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/avengers/avengers.csv", stringsAsFactors = FALSE)

av0 = av %>% filter(Name.Alias != "", Name.Alias != "Vance Astrovik")

av1 <- av0 %>% gather(key = Time, value = Death, c(11,13,15,17,19)) %>% select(Name.Alias, Time, Death)
av2 <- av0 %>% gather(key = Time, value = Return, c(12,14,16,18,20))  %>% select(Name.Alias, Time, Return)
av1 = av1 %>% mutate(Time = parse_number(Time))
av2 = av2 %>% mutate(Time = parse_number(Time))

av3 = left_join(av1, av2, by=c("Name.Alias", "Time"))

av3$Death = replace(av3$Death, av3$Death == "", NA)
av3$Return = replace(av3$Return, av3$Return == "", NA)

head(av3)
```

The following statement from the FiveThirtyEight, examined by Nathan:
There’s a 2-in-3 chance that a member of the Avengers returned from their first stint in the afterlife, but only a 50 percent chance they recovered from a second or third death.
```{r}

diedOnce = av3 %>% filter(Death == "YES", Time == 1)
returnedOnce = diedOnce %>% filter(Return == "YES")
nrow(returnedOnce) / nrow(diedOnce)

diedTwice = av3 %>% filter(Death == "YES", Time == 2)
returnedTwice = diedTwice %>% filter(Return == "YES")
nrow(returnedTwice) / nrow(diedTwice)

diedThrice = av3 %>% filter(Death == "YES", Time == 3)
returnedThrice = diedThrice %>% filter(Return == "YES")
nrow(returnedThrice) / nrow(diedThrice)
```

The statement claimed that Avengers have a 2/3 chance of coming back after they died, but the code shows that the real chance was about 70% which is slightly higher but still very close to the claimed value. The percentage of Avengers that cam back after their 2nd and 3rd deaths were 53% and 50% respectively. These values are incredibly close to the statement that the Avengers had a 1/2 chance of returning from a 2nd or 3rd death.


Yen:
"The MVP of the Earth-616 Marvel Universe Avengers has to be Jocasta — an android based on Janet van Dyne and built by Ultron — who has been destroyed five times and then recovered five times."

```{r}
av3 %>% filter(Name.Alias == "Jocasta")
```

From the above we gathered that Jocasta died five times and returned after every deaths.




