---
title: "homework9"
author: "Nathan Frank and Yen Wang"
date: "3/30/2022"
output: html_document
---

Team members: Nathan Frank and Yen Wang

Link to repo: https://github.com/natefrank48/homework9 



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


Data Tidying

```{r}
av <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/avengers/avengers.csv", stringsAsFactors = FALSE)

av0 = av %>% filter(Name.Alias != "", Name.Alias != "Vance Astrovik")

av1 <- av0 %>% gather(key = Time, value = Death, c(11,13,15,17,19)) %>% select(Name.Alias, Time, Death)
av2 <- av0 %>% gather(key = Time, value = Return, c(12,14,16,18,20))  %>% select(Name.Alias, Time, Return)
av1 = av1 %>% mutate(Time = parse_number(Time))
av2 = av2 %>% mutate(Time = parse_number(Time))

av3 = left_join(av1, av2, by=c("Name.Alias", "Time"))

av3$Death = replace(av3$Death, av3$Death == "", NA)
av3$Return = replace(av3$Return, av3$Return == "", NA)

head(av3)

```

The following statement from the FiveThirtyEight, examined by Nathan:

```{r}


```

Yen:
"The MVP of the Earth-616 Marvel Universe Avengers has to be Jocasta — an android based on Janet van Dyne and built by Ultron — who has been destroyed five times and then recovered five times."

```{r}
av3 %>% filter(Name.Alias == "Jocasta")

```

From the above we gathered that Jocasta died five times and returned after every deaths.


